Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-09-26 paper/paper.Rmd
remove sentence on custom_cv vs cv difference

Support for user-defined partitioning strategies is built into \pkg{mlr3} directly.
In this so-called "Custom CV", users supply a factor variable, each level of which defines a partition.
<!-- AB: I think we can omit this sentence, otherwise we would have to repeat it for the other LOBO methods as well. Here we're in the leave-ONE-something-out section. -->
<!--
This partitioning concept should not be mistaken with "group-level resampling" (section \@ref(sec:group-level)), which conducts additional combination of data splits and performs CV at the block level.
-->
The factor variable can either be specified through a factor vector of the same length as number of observations, or by passing the name of a feature of type `character` within the task (argument `col`).
The following simple example from `sperrorest::partition_factor()` creates altitudinal zones that define the spatial partitions.

>>>>

Support for user-defined partitioning strategies is built into \pkg{mlr3} directly.
In this so-called "Custom CV", users supply a factor variable, each level of which defines a partition.
The factor variable can either be specified through a factor vector of the same length as number of observations, or by passing the name of a feature of type `character` within the task (argument `col`).
The following simple example from `sperrorest::partition_factor()` creates altitudinal zones that define the spatial partitions.
